% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage{fancyvrb} %http://stackoverflow.com/questions/2212626/latex-adding-a-varying-amount-of-horizontal-spacing-to-the-beginning-of-each-n
\begin{document}

\name{Krishna P. Adhikari}
% \address used twice to have two lines of address
\address{7 Dorsey Rd Apt D, Newport News VA, 23606}
%\address{4707 Killam Ave, Apt B4, Norfolk, VA 23508}
\address{(757) 839 8594; \texttt{kadhi001@odu.edu}}

 
\begin{resume}
 
%\section{OBJECTIVE}   The position of postdoctoral fellow.    %Optional??? kp
				% The position of the Hall A postdoctoral fellow.    %Optional??? kp
                %A position in the field of computers with special interests in business 
                %applications programming, information processing, and management systems. 
 
 
\section{EDUCATION} %{\sl Bachelor of Science,} Interdisciplinary Science \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in 		% Computer Modern (default) font
              %  Rensselaer Polytechnic Institute, Troy, NY, expected December 1990 \\
              %  Concentration: Computer Science \\          Minor: Management 
              %
              %
    \textbf{Ph.D.}, Physics, Old Dominion University, Norfolk, VA, USA.  \hfill Dec 2013\\
    %\begin{Verbatim}
       \hspace*{5 mm} \textbf{Dissertation:} Measurement of the spin structure function $g^D_{1}$ \\
       \hspace*{10 mm} of the deuteron and its moments at low $Q^2$. \\
       \hspace*{5 mm} \textbf{Supervisor:} Dr. Sebastian E. Kuhn (\texttt{kuhn@jlab.org}) \\
    %\end{Verbatim}
    \textbf{M.S.}, Physics, Old Dominion University, Norfolk, VA, USA. \hfill 2006 \\ 
    \textbf{M.Sc.}, Physics, Tribhuvan University, Kathmandu, Nepal. \hfill 2000 \\ 
    \textbf{B.Sc.}, Physics, Mathematics, Chemistry, Tribhuvan University, Nepal. \hfill 1997 %\\ %\years{1997}


 
\section{COMPUTER \\ SKILLS} %{\sl Languages \& Software:} COBOL, IFPS, Focus, Megacalc, Pascal, Modula2, 
                %C, APL, SNOBOL, FORTRAN, LISP, SPIRES, BASIC, VSPC Autotab, IBM 370 Assembler, Lotus 1-2-3. \\
                %{\sl Operating Systems:} MTS, TSO, Unix.
                {\bf Operating Systems:} Microsoft Windows, Linux/Unix \\
                {\bf Languages:} C/C++, Fortran, Visual Basic, Java, Perl, bash, \\
                \hspace*{5 mm}tcsh, Makefile, CMake, HTML, JavaScript, LaTex \\ 
                {\bf Special Softwares:} ROOT, GSIM, GEANT4, Microsoft Office, \\
                \hspace*{5 mm} OpenOffice.org, SketchUp, Inkscape, JaxoDraw \\

\section{EXPERIENCE} 		{\bf Research Experience:} \\
		Postdoctoral Research Associate, Mississippi State University, \hfill Since Sep 2014\\
        %Working with JLab's HD-ice group as "Casual" TD-I \hfill Since Feb 2014\\
        HDice Technical Worker, Jefferson Lab, \hfill Feb - Aug 2014\\ %Onofficially, I started earlier (from Feb)
        %HDice Technical Worker, Jefferson Lab, \hfill May - Aug 2014\\  %officially
		Research Assistant, Physics, Old Dominion University \hfill 2007 - 2013 \\
		DOE/INFN Summer Exchange Student, INFN, Genoa, Italy \hfill 2009 \\
		Participated in studying Insolation and Photovoltaic system, TU, Nepal. \hfill 2003 \\
		Assisted a senior student in operating Brewer Spectrometer, TU, Nepal. \hfill 2000 \\
		{\bf Teaching Experience:} \\
		Teaching Assistant, Physics, Old Dominion University \hfill 2004 - 2007 \\
		Taught Physics at the undergraduate level as a part-time lecturer \\
		\hspace*{3 mm} at four different colleges in Kathmandu, Nepal. \hfill 2001 - 2004 \\
		Taught Science and Mathematics at the secondary school \\
		\hspace*{3 mm} level in Chitwan, Nepal.  \hfill 1997 - 1998
		 

 
\section{Leadership, \\ Community Service, \\ Affiliations} % Organized and directed the 1988 and 1989 Grand Marshall Week \newline ``Basketball Marathon.'' A 24 hour charity event to benefit the Troy Boys Club. Over 250 people participated each year. 
  {\bf Volunteering / Community Service: } \\
  Attended to ODU Physics Demos during multiple Norfolk Children \\
  \hspace*{3 mm} Festivals, and Open Houses at ODU and Jefferson Lab. \\
  Monarch Mentor to new International Students, Office of Inter-cultural \\
  \hspace*{3 mm} Relations, Old Dominion University, 2006.\\
  {\bf Leadership Activities: } \\
  Monarch Mentor Training (2006) and Big Leadership Training (2007) \\
  \hspace*{3 mm} (from the Office of Inter-cultural Relations, Old Dominion University).\\
  Helped found Nepali Student Community (NeSCo) at ODU \\
  \hspace*{3 mm} (served as the founding President) \\
	{\bf Other Affiliations: } \\
	American Physical Society; Nepal Physical Society (Life Member since \\
	\hspace*{3 mm} 2004); CLAS Collaboration (since 2007); Physics Graduate \\
	\hspace*{3 mm} Student Association (PGSA) at ODU (past member); Global \\
	\hspace*{3 mm} Student Friendship (GSF) at ODU (past member).

%\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            %Elected {\it House Manager}, Rho Phi Sorority \\    Elected {\it Sports Chairman} \\
            %Attended Krannet Leadership Conference \\         Headed delegation to Rho Phi Congress \\
            %    Junior varsity basketball team \\       Participant, seven intramural athletic teams 
 
\section{Languages} Nepali, English, Hindi
\end{resume}
\end{document}







